Git Learning Notes

### 2014-09-27 ch-intro/ch-intro.tex
outline adjusted 30%

\section{Background and Motivation: Nanomaterials for Energy Applications}
\today

TMO as electrochromic device and TMDC as newly 2D semiconductor, and some VLS.
Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could been used in solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism) applications.

\iffalse
Materials that human can make define the age they live in. From Stone Age to Bronze Age and Iron Age, people evolve as mastering more and more sophisticated techniques of manipulating metals, such as alloying and annealing. Obtaining extreme high purity of silicon brings us into Information Age. Future is difficult to predict. But nanotechnology is one direction that we can not ignore. According to \gls{nni}, \gls{nanotechnology}. This definition alludes that dimension comes before compositions. It is often related to the quantum confinement or surface area in nanomaterials, which we will later revisit with specific scenario.

There are three states of matter under usual conditions: solid,liquid and gas. Solids materials could be further categorized into five groups: metals, ceramics, polymers, semiconductors, and composites.\cite{William2009} This classification is based on both composition and mechanical, electrical, and thermal properties as well as the associated functionality(i.e., \gls{ceramics} are typically hard yet brittle, insulating to electricity and resistant to heating).

\fi
Energy saving and harvesting.

@@

\subsection{Advantage of Nano-engineering}

@@

\section{Dissertation Outline}
% what content should be presented

The materials studied in this work/dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and their chalcogenide counterparts (\ce{WS2} and \ce{MoS2}).

This dissertation primarily focuses on growth and characterization, and will only present some preliminary tests on device and applications. Experimental tools for growth and characterization will be introduced in Chapter 2. Chapter 3 will be devoted to tungsten oxides (\ce{WO3}) and sodium tungsten oxides (\ce{Na5W14O44}) nanowires, where the role of sodium compounds in metallic tungsten precursors are thoroughly investigated. Chapter 4 will turn to molybdenum oxides (\ce{MoO3}) growth using alkaline metal compounds as catalysts. In Chapter 5, the growth of \gls{tmdc} and heterostructures will be discussed. Emphasis will be placed on the characterization of individual \ce{WO3}-\ce{WS2} core-shell \gls{nw}. The dissertation is then concluded with a summary and future work.

\iffalse

We have synthesized \gls{tmo} and \gls{tmdc} at nanoscale, measured their crystalline structures and optical properties and demonstrated some devices assembled using as-synthesized nanomaterials. We aim to illustrate that by nanoengineering these \gls{tmo} and \gls{tmdc}, enhanced performances over their bulk states could be expected and new properties will arise. In the remaining sections of this chapter, we will discuss some general perspectives of nanomaterials, the growth apparatus and characterization methods that apply to all experiments done in this work. Then chapter 2 will focus on growth of \ce{WO3} and its derivative. We employed thermal \gls{cvd} to synthesize \ce{WO3} \gls{nw}, and we investigated the role of impurity in tungsten metallic powders, during which we observed a new state of sodium tungsten oxides: \ce{Na5W14O44} nanowires. We also found a method to potentially obtain large yield of \ce{WO3} \gls{nw}. Chapter 3 will concentrate on \ce{MoO3}. We explored two different growth mechanism of \ce{MoO3}:\gls{vs} and \gls{vls}. We discovered that alkaline oxides can be used as catalyst to grow two distinct \ce{MoO3} morphologies: nanobelts and towers. We further demonstrated the application of as-synthesized \ce{MoO3} nanomaterials in electrochromic devices.  In chapter 4 we discuss  We synthesized  and inspected the growth of \gls{fl} \ce{WS2}. Chapter 5 will conclude with an overall summary.

\fi

%\input{../end.tex} %  comment out when assembling

>>>>

\section{Background and Motivation: Nanomaterials for Energy Applications}

Transition metal generally refers to any elements in the d-block of periodic table, and transition metal oxides (TMOs) mean the chemical compounds that consist of at least one transition metal element and oxygen. Similarly, transition metal dichalcogenides (TMDCs) are compounds that combine at least one transition metal with chalcogen elements from group VIA (S, Se, Te, Po). Oxygen also belongs to group VIA, but is often treated separately. This study focused on the following three materials: molybdenum oxide, tungsten oxide and tungsten disulfide. Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$, respectively.

The two metal oxides, \ce{MoO3} and \ce{WO3}, have been studied for decades for energy related applications, e.g., photoelectrochemistry,\cite{Su2010} photocatalysis,\cite{Watcharenwong2008, Macphee2010} photovoltaics\cite{Coridan2013} and electrochromism.\cite{Yoshimura1985, Mortimer2011} \ce{WS2} has also been investigated in various forms, i.e., thin film, nanotube, and 2D atomic layer recently. \ce{WS2} exhibits some potentials in solar cell, water cleavage, and field effect transistor.

Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then electron-hole pairs generate free radicals, i.e., \ce{OH.}, which enable further reactions. For water splitting using solar energy, the band gap should be within $2.0 \sim 3.0 $ eV, and CB edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the VB top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
\begin{subequations}\label{eq:h2o}
\begin{align}
4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
\end{align}
\end{subequations}
As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2}(versus \gls{nhe}), and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}. So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone. Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
% wo3 vs NHE
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{woxnhe.jpg}
\caption[Bands positions of \ce{WO3} versus NHE]{Bands positions of \ce{WO3} in contact with aqueous electolyte at pH 1, adapted from Ref.\cite{Gratzel2001}}
\label{fig:woxnhe}
\end{figure}
Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}. The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}

\subsection{Advantages of Nano-Engineering}

@@

@@

\section{Objective and Scope}
To fully harvest the advantages of these TMO and TMDC one-dimensional nanomaterials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must first be established. Therefore, this dissertation primarily focuses on synthesis, growth mechanism study and characterization, and will only present preliminary results on device and applications.

\section{Dissertation Outline}
The materials studied in this dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and tungsten disulfide (\ce{WS2}). Experimental tools will be introduced in Chapter 2, including CVD apparatus and substrate treatments for growth, electron microscopes and optical spectrometers for characterization. Chapter 3 is devoted to tungsten oxides (\ce{WO3}) and sodium tungsten oxides (\ce{Na5W14O44}) nanowires, where the role of sodium in metallic tungsten precursors are thoroughly investigated; a potentially scalable growth method is also developed. Chapter 4 will turn to molybdenum oxide (\ce{MoO3}) growth using alkaline metal compounds as catalysts. In Chapter 5, a heterostructure based on \ce{WO3} \glspl{nw} is studied. Emphasis will be placed on the characterization of individual \ce{WO3}-\ce{WS2} core-shell \gls{nw}. The dissertation is then concluded with a summary and future work.

### 2014-09-27 ch-moox/moox.tex
outline adjusted 30%

% git version control added 012614
\chapter{Molybdenum Oxides}

@@

\section{Synthesis and Properties of Molybdenum Oxide}

@@

\subsection{Growth of Molybdenum Oxide}
Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures. Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}. Both methods have its own merits. Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time. Both methods are scalable for industrial applications. However the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method. Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one. The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures. \citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV. Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$). It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.

\subsection{Lattice Structures of Molybdenum Oxide and Molybdates}

@@

\subsection{Synthesis Methods in This Thesis}\label{sec:grow}

@@

In this section, the growth of \ce{MoO3} on bare Si substrates was presented first, followed by catalytic growth, both of which were characterized by SEM, XRD, TEM and EDX. Then the catalytic growth mechanism was investigated using \ce{NaOH} treated Si substrate.
\subsection{Growth on Si Substrate}\label{sec:nonsi}

@@

\subsection{Growth on NaOH-Si Substrate}\label{sec:naohsi}

@@

\subsection{Verification of Growth Model}

@@

\section{Extension of Alkaline Metal Catalyzed Growth}
\subsection{Growth on Alkaline Metal Containing Substrate}
In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkaline metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature. This fact allows for the usage of a variety of alkaline metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}. Some experiments have been performed in this study, including growth using KI and \ce{Na2CO3} treated Si substrate, glass and mica. Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and towers on ITO glass, respectively. Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas the towers on ITO glass exhibit stacking features.

@@

\subsection{Liquid Exfoliation of Molybdenum Oxide}

>>>>

% git version control added 012614
\chapter{New Vapor-Solid-Solid Growth Modes of Molybdenum Oxide}

@@

\subsection{Properties and Applications of Molybdenum Oxide}

@@

@@

\subsection{Synthesis Review of Molybdenum Oxide}
Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures. Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}. Both methods have its own merits. Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time. Both methods are scalable for industrial applications. However the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method. Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one. The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures. \citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV. Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$). It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.

\section{Experimental}\label{sec:grow}

@@

In this section, the growth of \ce{MoO3} on bare Si substrates was presented first, followed by catalytic growth, both of which were characterized by SEM, XRD, TEM and EDX. Then the catalytic growth mechanism was investigated using \ce{NaOH} treated Si substrate.
\subsection{Non-catalyst Growth}\label{sec:nonsi}

@@

\subsection{Catalyst-assisted Growth}\label{sec:naohsi}

@@

@@

\subsection{Growth on Alkaline Metal Containing Substrate}
In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkaline metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature. This fact allows for the usage of a variety of alkaline metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}. Some experiments have been performed in this study, including growth using KI and \ce{Na2CO3} treated Si substrate, glass and mica. Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and towers on ITO glass, respectively. Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas the towers on ITO glass exhibit stacking features.

@@

\subsection{Optical Properties of Molybdenum Oxide}
